---
title: "DDP Week4 Assignment"
author: "Damian Strzelec"
date: "11/24/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Analysis Description

- Goal:
Create Shiny Application project including R code algorithm based on selected new data set

- Introduction: 
Airquality data set is summarizing daily readings of the following air quality values for May 1, 1973 to September 30, 1973.

- Assumptions:
Analysis includes proposal of two linear regression models for ozone prediction based on wind values. 

- Results:
Model 1 is more accurate. Ozone predictions changes are significantly related for wind between 1mph and 10mph.
Model 2 is applicable only for wind values from 1 to 17 mph.



## Airquality Dataset Summary
```{r airquality, echo = TRUE}
summary(airquality)
```

## Define code ui.R

```r
shinyUI(fluidPage(
    titlePanel("Analysis of Ozone based on Wind"),
    sidebarLayout(
        sidebarPanel(
            sliderInput("sliderWind", "What is the Wind [mph] value?",
            1, 21, value = 10),
            checkboxInput("showModel1", "Show/Hide Model 1", value = TRUE),
            checkboxInput("showModel2", "Show/Hide Model 2", value = TRUE)
        ),
        mainPanel(
            plotOutput("plot1"),
            h3("Ozone Prediction from Model 1:"),
            textOutput("pred1"),
            h3("Ozone Prediction from Model 2:"),
            textOutput("pred2"),
        ))))
```

## Define code server.R

```r
shinyServer(function(input, output) {
airquality$Wind1 <- ifelse(airquality$Wind - 10> 0, airquality$Wind - 10,0)
    model1 <- lm(Ozone ~ Wind, data = airquality)
    model2 <- lm(Ozone ~ Wind1 + Wind, data = airquality)
    
    model1pred    <- reactive({
        WindInput <- input$sliderWind
        predict(model1, newdata = data.frame(Wind = WindInput)) })
        
    model2pred    <- reactive({
        WindInput <- input$sliderWind
        predict(model2, newdata = data.frame(Wind = WindInput,
                Wind1 = ifelse(WindInput - 10 > 0,WindInput - 10, 0))) })
    ....
    
     output$pred1 <- renderText({model1pred() })
     output$pred2 <- renderText({model2pred() })
}) 
```




